More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2018-09-14 2016-Weak-FH-Bisim/WeakBisim.tex
during meeting

\section*{Status and TODO list}
TODOS et deadline

@@

\item \TODO{uniformiser pNet \pNet pNet s \pNet s (dans le texte et les formules!)}

\item \TODO{proposition Ludo \& Rabea: \pNet -> P,Q dans les formules pour que ce soit moins long}
\item related works
\end{itemize}
Ludo:
\begin{itemize}
\item[X] reorga sec weak bisim + thm -> 10 Juil
\item[X]  intro et orga globale du papier -> fin aout
\item[NEW] explication dans semantique open pnets et composition
\end{itemize}

@@

Eric
\begin{itemize}
\item nettoyage -> 5 juil
\item example -> fin aout -> qq transitions dans l abp
%\item re-ecrire transitions page 14 comment les presenter?
%\item arbre de deduction
%\item exemple avec actions
\end{itemize}
%=== 20 Avril?
\medskip

Rabea
\begin{itemize}
\item preuve transitivite -> 10 juil
\item proofs of new theorems -> fin juillet
%\item [x] uniformiser p et P pour les pnets 
%\item [x] relectures
\end{itemize}

@@

\begin{theorem}[Context equivalencefor  weak bisimulation]\label{weak-thm-ctxt-eq}
	Consider two weak FH-bisimilar open pNets:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
	\Sort_j^{j\in 
	J}, 	\overline{\symb{SV'}}\myrangle$ 
	(recall they must have the same holes to be bisimilar).
	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet'[Q]_{j_0}$ are weak FH-bisimilar.
\end{theorem}

@@

\TODO{Here we should include:
  %% \\  - A sufficient condition for an open PNet to preserve Weak-FH,
  %% including: 1) no non-deterministic Tau-choice in the pLTSs, 2) a
  %% synch vector propagating Tau from a subnet $pNet_i$ mandatory
  %% everytime $pNet_i$ can do some visible action in the current
  %% context, 3) if we have a vector <Tau, -, a, - > --> b with ``a'' a visible
  %% action of some CLOSED subnet, then b=Tau. 
  \\  - the corresponding Congruence theorem
  \\- An example
}

@@

\section{Proof of associativity of Enable pNet.}
\label{appendix:assoc}

Using the usual encoding of the Lotos Enable operator (see
Fig. \ref{schema:ABP-pnets}), we build now open automata for two  
open pNets \texttt{P>>(Q>>R)} and \texttt{(P>>Q)>>R)}, and 
prove their bisimilarity.
\begin{figure}[t]
\centerline{ % \includegraphics[width=0.5\linewidth]{XFIG/Struct-P-QR}
% \includegraphics[width=0.35\linewidth]{XFIG/Struct-PQ-R}}
  \includegraphics[width=0.60\linewidth]{XFIG/P-QR}
  \hspace{5mm}
 \includegraphics[width=0.27\linewidth]{XFIG/PQ-R}}
  \caption{Structure of the pNets for ``P>>(Q>>R) and (P>>Q)>>R''}
  \label{schema:enable-assoc}
\end{figure}

The two open pNets are drawn in Fig. \ref{schema:enable-assoc}. To
alleviate the drawing, we have only 
  given one instance (C2) of the enable controller pLTSs, and one example of
  the set of synchronisation vectors.

  Below we give the two open automata for these pNets. In the
  open-transitions in these 
    automata, the predicates are very simple, and for readability
    we show them directly in the transitions.
    Remark that while the structure of the automaton states is useful
    for their construction, it is not relevant later, so we have
    dropped this structure when drawing the automaton.

\begin{figure}[h]
  \begin{minipage}{2cm}
  \includegraphics[width=\linewidth]{XFIG/PQR-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{7cm}
  \begin{eqnarray*}
    OT_1 & = \openrule{0 \xrightarrow{l}_{C_3} 0
    	\\\xrightarrow{a1}_P\\ a1\neq\delta(x)}
    {\ostate{00} \OTarrow{a1} \ostate{00}}\\
    OT_2 & = \openrule{
                       0 \xrightarrow{\delta}_{C_3} 1, ~~
                            0 \xrightarrow{l}_{C_4} 0,  ~~                 
                            \{\xrightarrow{\delta(x1)}_P, ~~
                            \xrightarrow{acc(x1)}_Q\}
                      }
                      {\ostate{00} \OTarrow{\underline{\delta(x1)}} \ostate{10}}    \\
    OT_3 & = \openrule{0 \xrightarrow{l}_{C_4} 0,
                        \\1 \xrightarrow{r}_{C_3} 1,\\
                        \xrightarrow{a2}_Q,\\a2\neq\delta(x)
                        }
    {\ostate{10} \OTarrow{a2} \ostate{10}}\\
    OT_4 & = \openrule{
                       0 \xrightarrow{\delta}_{C_4} 1, \qquad
                       1 \xrightarrow{r}_{C_3} 1, \qquad
                       \{\xrightarrow{\delta(x2)}_Q, \qquad 
                       \xrightarrow{acc(x2)}_R\} 
                       }
                      {\ostate{10} \OTarrow{\underline{\delta(x2)}} \ostate{11}}    \\
    OT_5 & = \openrule{1 \xrightarrow{r}_{C_3} 1, \\1 \xrightarrow{r}_{C_4} 1, 
    	\\\xrightarrow{a3}_R
    	}
    {\ostate{11} \OTarrow{a3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
  \caption{Open Automaton for the term ``P>>(Q>>R)''}
  \label{schema:enable3bis}
\end{figure}

\begin{figure}[t]
  \begin{minipage}{2cm}
  \includegraphics[width=\linewidth]{XFIG/PQR2-automaton}
  \end{minipage}
  \hspace{10mm}
  \begin{minipage}{7cm}
  \begin{eqnarray*}
    OT'_1 & = \openrule
             {
               0 \xrightarrow{l}_{C_3} 0,~~0 \xrightarrow{l}_{C_4} 0,~~
               \{\xrightarrow{b1}_P\},~~ b1\neq\delta(y)
               }
             {\ostate{00} \OTarrow{b1} \ostate{00}}\\
    OT'_2 & = \openrule
             {
                       0 \xrightarrow{l}_{C_5} 0, ~~
                       0 \xrightarrow{\delta}_{C_6} 1,  ~~
              \{\xrightarrow{\delta(y1)}_P,~~      \xrightarrow{acc(y1)}_Q\}~~ 
                      }
             {\ostate{00} \OTarrow{\underline{\delta(y1)}} \ostate{01}}\\
    OT'_3 & = \openrule
             {
               0 \xrightarrow{l}_{C_5} 0,\\0 \xrightarrow{r}_{C_6} 0,
               \\ \{\xrightarrow{b2}_Q\},\\b2\neq\delta(y)
               }
    {\ostate{01} \OTarrow{b2} \ostate{01}}\\
    OT'_4 & = \openrule
             {
                       0 \xrightarrow{\delta}_{C_5} 1, ~~
                       1 \xrightarrow{r}_{C_6} 1, ~~\{\xrightarrow{\delta(y2)}_Q, ~~
                    \xrightarrow{accept(y2)}_R\} 
                                 }
             {\ostate{01} \OTarrow{\underline{\delta(y2)}} \ostate{11}}    \\
    OT'_5 & = \openrule
             {1 \xrightarrow{r}_{C_5} 1,\\\{\xrightarrow{b3}_R\}
             	}
             {\ostate{11} \OTarrow{b3} \ostate{11}}
    \end{eqnarray*}
  \end{minipage}
%  \label{schema:enable5}
\end{figure}

In this example, we have no state variables in the pNets leaves, so we
need no auxiliary predicate in the FH-bisimulation.

Let us build a relation
    $R = \{(A1_0,A2_0), (A1_1,A2_1), (A1_2,A2_2)\}$, and prove that
    $R$ is a strong FH-bisimulation.

    Pick e.g. transition $OT_1$ of automaton $A1$, we have
    $A1_0 \xrightarrow{OT_1}_{A1} A1_0$. The matching transition from
    $A2_0$ is $OT'_1$, with 
    $A2_0 \xrightarrow{OT'_1}_{A2} A2_0$, the set of holes involved in
    both transitions is $\{P\}$, and the resulting state is in the
    bisimulation ($A1_0 ~ A2_0$).
    The proof obligation is:

    $$  a1\neq\delta(x) \implies
         a1=b1 \implies b1\neq\delta(y) \land a1=b1 $$

    The proof obligation for $OT_2$ versus $OT'_2$ is still simpler:

    $$ \delta(x_1)=\delta(y_1) \land acc(x_1)=acc(y_1)
       \implies \underline{\delta(x_1)}=\underline{\delta(y_1)} $$

       the 3 other cases, and the 5 in the other direction, are left
       to the reader. All are simple to prove, so $R$ is a
       FH-bisimulation, and the initial states of the 2 pNets are equivalent.
           \qed

       This proof shows how the flattening induced by the open transitions makes the 
       reasoning on hierarchical structures easy, while keeping a structured view of the 
       compared systems.

>>>>

\section*{Status and TODO list}
Conventions
[14/9/2018]

Dans le texte pas de $\backslash$ devant pNet et pLTS

pNet devient P ou Q dans les equations; on garde $pLTS$

TODOS et deadline

@@

\item related works
\end{itemize}
Ludo:
\begin{itemize}
\item[X] reorga sec weak bisim + thm -> 10 Juil
\item[X]  intro et orga globale du papier -> fin aout
\item[partial] explication dans semantique open pnets et composition
\item uniformisation pNet P Q
\end{itemize}

@@

Eric
\begin{itemize}
\item[X] nettoyage (1/2) -> 5 juil
\item nettoyage exemple et algo de calcul
\item example -> fin aout -> qq transitions dans l abp
%\item re-ecrire transitions page 14 comment les presenter?
%\item arbre de deduction
%\item exemple avec actions
\end{itemize}

Rabea
\begin{itemize}
\item preuve transitivite -> 20 sept
\item proofs of new theorems -> oct?
%\item [x] uniformiser p et P pour les pnets 
%\item [x] relectures
\end{itemize}

@@

\begin{theorem}[Context equivalence for  weak bisimulation]\label{weak-thm-ctxt-eq}
	Consider two weak FH-bisimilar open pNets:
	$\pNet = \mylangle \pNet_i^{i\in I}, \Sort_j^{j\in J}, 
	\overline{\symb{SV}}\myrangle$ and 	$\pNet' = \mylangle {\pNet'}_i^{i\in I}, 
	\Sort_j^{j\in 
	J}, 	\overline{\symb{SV'}}\myrangle$ 
	(recall they must have the same holes to be bisimilar).
	Let $j_0\in J$ be a hole, and $Q$ be a pNet such that $\Sortop(Q)=\Sort_{j_0}$. Then 
	$\pNet[Q]_{j_0}$ and 
	$\pNet'[Q]_{j_0}$ are weak FH-bisimilar.
\end{theorem}

@@

@@
